### 2022-10-14 Papers/PaperForReview.tex
Initial commit for proposal paper tex files. Currently only added the introdution.

% CVPR 2023 Paper Template
% based on the CVPR template provided by Ming-Ming Cheng (https://github.com/MCG-NKU/CVPR_Template)
% modified and extended by Stefan Roth (stefan.roth@NOSPAMtu-darmstadt.de)

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
\usepackage[final]{cvpr}      % To produce the REVIEW version
%\usepackage{cvpr}              % To produce the CAMERA-READY version
%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{*****} % *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2022}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{The Shot Predictor}

\author{Laith Altarabishi\\
University of Texas at Austin\\
{\tt\small <insert email>}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Sidharth Babu\\
University of Texas at Austin\\
{\tt\small <insert email>}
\and
Afnan Mir \\
University of Texas at Austin\\
{\tt\small afnanmir@utexas.edu}
\and
Zayam Tariq \\
University of Texas at Austin\\
{\tt\small <insert email>}
}
\maketitle

%%%%%%%%% ABSTRACT

%%%%%%%%% BODY TEXT
\section{Problem Description}
\label{sec:intro}

In basketball, the ability of a player to effectively shoot the basketball typically comes down to the player’s shooting form. While the form of the best shooters tend to look different, they all typically use the same fundamentals. In our project, we will attempt to capture these fundamental aspects of a player’s shooting form and attempt to predict the outcome of a shot using these features. Research has been done on extracting features from a player’s movement to classify the action a player is performing (shooting, dribbling, etc.) [1], but we would like to focus our energy on feature extraction from the shooting motion using pose estimation [2], object detection [3], and possibly other methods to extract feature descriptors of a shot and attempt to identify it as a make or a miss.\\
\indent This problem is a particularly nontrivial application of pose estimation for two main reasons. The first being that there are multiple stages to
a basketball shot that need to be taken into account. From dipping the ball to waist level, to the motion of bringing the ball to eye level, to releasing the ball, each
plays a significant role in the outcome of a shot, so each stage needs to be taken into account. The second reason is the variability of the average shot. It can be argued that no two shots are identitical, when taking into account the speed of the shot
and different shooting forms. This will require us to develop a method of capturing all the motions of a shot in a way that is invariant to the shot's speed and overall form.

%-------------------------------------------------------------------------
%------------------------------------------------------------------------
\section{Related Works}
\label{sec:formatting}

All text must be in a two-column format.
The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
The second and following pages should begin 1 inch (2.54 cm) from the top edge.
On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
high.
%
Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
The \LaTeX\ template takes care of this when used properly.

%-------------------------------------------------------------------------
\subsection{Type style and fonts}

Wherever Times is specified, Times Roman may also be used.
If neither is available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE.
Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
Leave two blank lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type.
This information is to be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT.
Type main text in 10-point Times, single-spaced.
Do NOT use double-spacing.
All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
Make sure your text is fully justified---that is, flush left and flush right.
Please do not place any additional blank lines between paragraphs.

Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-, second-, and third-order headings.

FIRST-ORDER HEADINGS.
(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS.
(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote{This is what a footnote looks like.
It often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{Cross-references}

For the benefit of author(s) and readers, please use the
{\small\begin{verbatim}
  \cref{...}
\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
This will automatically insert the appropriate label alongside the cross-reference as in this example:
\begin{quotation}
  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
\end{quotation}
If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
{\small\begin{verbatim}
  \Cref{...}
\end{verbatim}}
command. Here is an example:
\begin{quotation}
  \Cref{fig:onecol} is also quite important.
\end{quotation}

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
When referenced in the text, enclose the citation number in square brackets, for
example~\cite{Authors14}.
Where appropriate, include page numbers and the name(s) of editors of referenced books.
When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
If you use the template as advised, this will be taken care of automatically.

\begin{table}
  \centering
  \begin{tabular}{@{}lc@{}}
    \toprule
    Method & Frobnability \\
    \midrule
    Theirs & Frumpy \\
    Yours & Frobbly \\
    Ours & Makes one's heart Frob\\
    \bottomrule
  \end{tabular}
  \caption{Results.   Ours is better.}
  \label{tab:example}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.
In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
Instead use
{\small\begin{verbatim}
  \centering
\end{verbatim}}
at the beginning of your figure.
Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.pdf}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.

If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit your finished paper.
We MUST have this form before your paper can be published in the proceedings.

Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
\url{https://www.computer.org/about/contact}.

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

### 2022-10-16 Papers/PaperForReview.tex
pose estimation section

@@
 University of Texas at Austin\\
-{\tt\small <insert email>}
+{\tt\small laithaustin@utexas.edu}
 % For a paper whose authors are all at the same institution,
@@
 
-All text must be in a two-column format.
-The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
-Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
-The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
-The second and following pages should begin 1 inch (2.54 cm) from the top edge.
-On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
-for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
-page.
+%-------------------------------------------------------------------------
+\subsection{Pose Estimation}
 
-%-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
-high.
+Pose Estimation is a critical topic in computer vision that will intersect with our goal of trying to accurately capture the motion and actions of a person taking a shot in basketball.
+Pose estimation, in the context of 2D videos of humans, is the problem of localizing anatomical keypoints or joints in a frame by frame video or image [2].
+To fulfill our goal of predicting the outcome of a basketball shot, it will be critical to assess the form of a player who's taking a shot - where form can be decomposed into various classifications of joints in space.
+Pose estimation methods can be categorized into bottom-up or top-down methodologies.
+Bottom-up methodologies start by estimating keypoints and body joints first, and then these points are clustered to form poses.
+In contrast,
+top-down methodologies of pose estimation first run a person detector before decomposing each person into their respective body joints within detected bounding boxes [10].
+Computational complexity is a major consideration for landmark pose estimation algorithms, and modern SOTA pose estimation algorithms deploy deep learning and CNNs to improve compuational overhead and speed [2].
+We list some examples of prevalent and SOTA pose estimation models that have been employed and researched below.
 %
-Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
-The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
-The \LaTeX\ template takes care of this when used properly.
+\begin{quotation}
+  OpenPose: The first multi-person realtime 2D pose estimation system that uses a bottom-up approach that implements nonparametric representation to associate human keypoints and body parts with an individual in an image [2].
+\\
+  \newline
+  \indent DeepPose: SOTA pose estimation method that uses DNNs to classify human body joints through the usage of cascading DNN regressors that produce high precision pose estimates [4]. \\
+  \newline
+  \indent AlphaPose: Multi-person SOTA realtime pose estimation system that outperforms OpenPose in AP score and has a high mAP score [9]. \\
+  \newline
+  \indent DeepCut: Proposes an approach to solving issues in both pose estimation and detection by using a partitioning and labeling formulation of a set of CNN part detectors [11].
+\end{quotation}
+%
 

### 2022-10-16 Papers/PaperForReview.tex
Add General Overview of Methdology

--- 2022-10-14 Papers/PaperForReview.tex
@@
 %------------------------------------------------------------------------
-\section{Final copy}
+\section{Methodology}
+\subsection{General Overview}
+We will have a camera taking in video input of a player shooting the basketball, potentially from two different angles.
+One angle would be a side view of the shooter that can capture the relative positions of the shooter and the hoop, and the other
+would be a head-on view of the of the shooter to capture the full pose estimation of the shooter.
 
-You must include your signed IEEE copyright release form when you submit your finished paper.
-We MUST have this form before your paper can be published in the proceedings.
-
-Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
-\url{https://www.computer.org/about/contact}.
+In the background, we will have our pose estimation algorithm running to capture the pose estimation of the shooter which will be used
+to make our predictions. Additionally, we will potentially be retrieving other data to create our feature vector, including the angle relationship
+between the shooter and the hoop, and the speed of the shot. We will be attempting to capture the pose estimation at multiple stages of the
+shot, as each stage can have a significant impact on the outcome of the shot. We will then take this feature vector and put it through a classification model.
+We will perform binary classification and predict whether a shot will go in or not.
 

### 2022-10-16 Papers/PaperForReview.tex
Finish methodology and timeline

@@
 University of Texas at Austin\\
-{\tt\small <insert email>}
+{\tt\small sidharth.n.babu@utexas.edu}
 \and
@@
 
+\subsection{Pose Estimation}
+As far as pose estimation goes, it seems that a bottom up approach to pose estimation will be the best approach for our use case, as the bottom up approach is the
+current state of the art when it comes to pose estimation and is computationally less expensive [12].
+There are a few state of the art bottom up pose estimation libraries that we could potentially use.
+These
+libraries include OpenPose, AlphaPose, DeepCut, and MoveNet. We will test these libraries on their latency and accuracy. With a basketball shot, we want minimum latency
+as well as an ability to run at a high frames per second (FPS) quantity. We will use these metrics as well as an accuracy score on a validation set to determine which pose
+estimation library to use. Once the library is decided, we will include this library into our pipeline to create features from our input video.
+
+\subsection{Feature Extraction and Classification}
+Before we get into creating features, we need to define how we want to create features using continuous video.
+There are three stages we can define: the loading of the shot, the propulsion of the ball from below the waist
+to eye-level, and the release. At these three different stages, we can define three methods for creating feature vectors.
+
+When the shooter loads the ball, the general pose/angle between specific key points is all that matters. However, this stage can take different amounts of time. To combat this,
+we can take the average of each desired angle for the whole time the shooter is at this stage.
+
+When the shooter is bringing the ball from the loading point to the release point, the movement is more important than key points.
+For example, the movement should not be too fast, and it should generally be straight up.
+Therefore, it would be optimal for us to generate a movement vector for each key point we care about, and also encode the speed component to vectorize this motion.
+
+When the ball is released, the general pose is again more important.
+Additionally, we would like to encode information about the angles between the hoop and the shooter's release point.
+So, for this case, we
+will again use angles of specific key points that we care about in our feature vector as well as information about the relation between the hoop and the shooter.
+
+To perform binary classification, there are two methods we can use.
+We could either concatenate all of these feature vectors and input it into one big classification model that will perform the prediction.
+Alternatively,
+we could put each feature vector through its own classification model and perform some form of weighted majority voting to make our prediction. Both will be tested to determine which method to use.
+
+We can also test various techniques of classification to see which performs the best.
+We can test between Logistic Regression, Support Vector Machine, Random Forest, and an MLP model.
+We can use cross validation to determine which
+of these model types will be optimal for us.
+
+\subsection{Training Procedures}
+In order to train our model(s), we will create our own training data by having a subject shoot free throws numerous times, capturing the feature vectors and labelling the data as makes or misses.
+
+\section{Timeline}
+We propose the following timeline, where week 1 represents the week of October 17th:
+\begin{itemize}
+  \item Week 1: \begin{itemize}
+    \item Familiarize ourselves with pose estimation libraries and how to use them.
+    \item Perform tests on each pose estimation library to determin which library to use
+  \end{itemize}
+  \item Week 2: \begin{itemize}
+    \item Collect training data of free throws
+    \item Test our pose estimation library on training data and see the data that we can obtain.
+  \end{itemize}
+  \item Week 3, 4, and 5: \begin{itemize}
+    \item Develop algorithm for feature extraction from shot motion
+    \item Test different types of classification on the data and determine which model to use
+  \end{itemize}
+  \item Week 6: \begin{itemize}
+    \item Evaluate/test final model
+    \item Write final report
+  \end{itemize}
+\end{itemize}
+
 %%%%%%%%% REFERENCES

### 2022-10-17 Papers/PaperForReview.tex
related works for basketball postures

@@
 University of Texas at Austin\\
-{\tt\small <insert email>}
+{\tt\small zayamtariq@utexas.edu}
 }
@@
 %
+
+Before a posture recognition algorithm can be made, though, there needs to be an understanding of what postures we are trying to recognize [1]. One example solution is shown below. 
+%
+\begin{quotation}
+  Level 1: Divide posture into two categories based on whether or not the motion is cyclic \\
+  \indent - Instantaneous Movement 
+  \indent - Continuous Movement 
+  \newline
+  \indent Level 2: Divide posture into seven postures \\
+  \indent - Walking 
+  \indent - Running 
+  \indent - Dribbling 
+  \indent - Jumping 
+  \indent - Shooting 
+  \indent - Passing 
+  \indent - Catching 
+\end{quotation}
+%
+
+Notice how these actions are exclusive to basketball. The algorithm is only concerned with basketball, and will deem all other actions as unnecessary as such.
 

### 2022-10-17 Papers/PaperForReview.tex
added a little bit about SIFT
2.2 object detection

@@
 Notice how these actions are exclusive to basketball. The algorithm is only concerned with basketball, and will deem all other actions as unnecessary as such. 
+A popular tool used for key feature detection in order to track certain postures is SIFT [1]. The upper and lower limbs are pivotal in determining what an athlete is doing, 
+so using SIFT to identify and track limbs would be useful for understanding an athlete's posture.
 
 %-------------------------------------------------------------------------
-\subsection{Type style and fonts}
+\subsection{Object Detection}
 
-Wherever Times is specified, Times Roman may also be used.
-If neither is available on your word processor, please use the font closest in
-appearance to Times to which you have access.
+Our project will hope to capture and detect objects in high frame-rate video, with minimal computational overhead so that we are able to best assess the keypoints/human joints of our basketball shooters.
+In recent years, object detection algorithms have evolved greatly and most SOTA models today utilize deep learning to provide more robust results [13].
+There are many pre-existing SOTA object detection methods that have been utilized in the context of pose estimation methods and regression issues, and the following works are examples of some of them.
 
-MAIN TITLE.
-Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
-The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
-do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
-Leave two blank lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type.
-This information is to be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT.
-Type main text in 10-point Times, single-spaced.
-Do NOT use double-spacing.
-All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
-Make sure your text is fully justified---that is, flush left and flush right.
-Please do not place any additional blank lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
-Short captions should be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-, second-, and third-order headings.
-
-FIRST-ORDER HEADINGS.
-(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS.
-(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
-If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote{This is what a footnote looks like.
-It often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
-If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
-Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{Cross-references}
-
-For the benefit of author(s) and readers, please use the
-{\small\begin{verbatim}
-  \cref{...}
-\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
-This will automatically insert the appropriate label alongside the cross-reference as in this example:
 \begin{quotation}
-  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
-  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
-  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
+  YOLO: Single stage object detection algorithm that frames detection as a regression problem to spatially seperated bounding boxes and associated class probabilities [3].\\
+  \newline
+  \indent Mask R-CNN: Two-stage object detection algorithm that detects objects in an image while creating high-quality segmentation masks for each instance [14].\\
+  \newline
+  \indent Feature Pyramid Networks: Two-stage object detection algorithm that uses the multi-scale, pyramidial hierarchy of deep convolutional networks to create feature pyramids [15]. \\
 \end{quotation}
-If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
-{\small\begin{verbatim}
-  \Cref{...}
-\end{verbatim}}
-command. Here is an example:
-\begin{quotation}
-  \Cref{fig:onecol} is also quite important.
-\end{quotation}
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
-When referenced in the text, enclose the citation number in square brackets, for
-example~\cite{Authors14}.
-Where appropriate, include page numbers and the name(s) of editors of referenced books.
-When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
-If you use the template as advised, this will be taken care of automatically.
-
-\begin{table}
-  \centering
-  \begin{tabular}{@{}lc@{}}
-    \toprule
-    Method & Frobnability \\
-    \midrule
-    Theirs & Frumpy \\
-    Yours & Frobbly \\
-    Ours & Makes one's heart Frob\\
-    \bottomrule
-  \end{tabular}
-  \caption{Results.   Ours is better.}
-  \label{tab:example}
-\end{table}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.
-In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
-Instead use
-{\small\begin{verbatim}
-  \centering
-\end{verbatim}}
-at the beginning of your figure.
-Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
-Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
-Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
-You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.pdf}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.
-
-If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
-Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.
 

### 2022-10-17 Papers/PaperForReview.tex
basketball + pose detection paper

@@
 
-Before a posture recognition algorithm can be made, though, there needs to be an understanding of what postures we are trying to recognize [1]. One example solution is shown below. 
+%-------------------------------------------------------------------------
+\subsection{Basketball and Pose Estimation}
+
+Collecting and analyzing basketball player's posture data is important and 
+highly sought after in the scientific basketball community in order to help
+coaches improve their training plan, and help players maximize their training 
+outputs. As it stands, the current technology faces some combination of 
+high inefficiency or high error rates. Rather than using wearable, inertial sensor
+recognition equipment, which tends to be expensive and not applicable to how a 
+real game is played, it was decided to use posture recognition via video instead.
+In order to improve the athlete's training effect, a gesture recognition method 
+based on feature extraction and machine learning was implemented in order to 
+acquire the upper limb and lower limb features needed to classify a posture.  
+The action posture data of players was collected through image feature extraction
+methods, and with the method of feature selection, accurate classification and recognition
+of basketball shooting gestures can be made. This paper is similar to our project because 
+it attempts to take and encode data about motion of a player through pose estimation to 
+make predictions, but our project solely focuses on the motion of a shot, and predicting 
+the outcome of the shot.
+
 %
-\begin{quotation}
-  Level 1: Divide posture into two categories based on whether or not the motion is cyclic \\
-  \indent - Instantaneous Movement 
-  \indent - Continuous Movement 
-  \newline
-  \indent Level 2: Divide posture into seven postures \\
-  \indent - Walking 
-  \indent - Running 
-  \indent - Dribbling 
-  \indent - Jumping 
-  \indent - Shooting 
-  \indent - Passing 
-  \indent - Catching 
-\end{quotation}
-%
-
-Notice how these actions are exclusive to basketball. The algorithm is only concerned with basketball, and will deem all other actions as unnecessary as such. 
-A popular tool used for key feature detection in order to track certain postures is SIFT [1]. The upper and lower limbs are pivotal in determining what an athlete is doing, 
-so using SIFT to identify and track limbs would be useful for understanding an athlete's posture.
 

### 2022-11-28 Papers/Proposal/PaperForReview.tex
Add a proposal folder and move all proposal document contents to that folder

--- 2022-10-17 Papers/PaperForReview.tex
@@
 In our project, we will attempt to capture these fundamental aspects of a player’s shooting form and attempt to predict the outcome of a shot using these features.
-Research has been done on extracting features from a player’s movement to classify the action a player is performing (shooting, dribbling, etc.) [1], but we would like to focus our energy on feature extraction from the shooting motion using pose estimation [2], object detection [3], and possibly other methods to extract feature descriptors of a shot and attempt to identify it as a make or a miss.\\
+Research has been done on extracting features from a player’s movement to classify the action a player is performing (shooting, dribbling, etc.) \cite{Basketball}, but we would like to focus our energy on feature extraction from the shooting motion using pose estimation \cite{OpenPose}, object detection \cite{YOLO}, and possibly other methods to extract feature descriptors of a shot and attempt to identify it as a make or a miss.\\
 \indent This problem is a particularly nontrivial application of pose estimation for two main reasons. The first being that there are multiple stages to
@@
 Pose Estimation is a critical topic in computer vision that will intersect with our goal of trying to accurately capture the motion and actions of a person taking a shot in basketball.
-Pose estimation, in the context of 2D videos of humans, is the problem of localizing anatomical keypoints or joints in a frame by frame video or image [2].
+Pose estimation, in the context of 2D videos of humans, is the problem of localizing anatomical keypoints or joints in a frame by frame video or image \cite{OpenPose}.
 To fulfill our goal of predicting the outcome of a basketball shot, it will be critical to assess the form of a player who's taking a shot - where form can be decomposed into various classifications of joints in space.
@@
 In contrast,
-top-down methodologies of pose estimation first run a person detector before decomposing each person into their respective body joints within detected bounding boxes [10].
-Computational complexity is a major consideration for landmark pose estimation algorithms, and modern SOTA pose estimation algorithms deploy deep learning and CNNs to improve compuational overhead and speed [2].
+top-down methodologies of pose estimation first run a person detector before decomposing each person into their respective body joints within detected bounding boxes \cite{Viso2}.
+Computational complexity is a major consideration for landmark pose estimation algorithms, and modern SOTA pose estimation algorithms deploy deep learning and CNNs to improve compuational overhead and speed \cite{OpenPose}.
 We list some examples of prevalent and SOTA pose estimation models that have been employed and researched below.
@@
 \begin{quotation}
-  OpenPose: The first multi-person realtime 2D pose estimation system that uses a bottom-up approach that implements nonparametric representation to associate human keypoints and body parts with an individual in an image [2].
+  OpenPose: The first multi-person realtime 2D pose estimation system that uses a bottom-up approach that implements nonparametric representation to associate human keypoints and body parts with an individual in an image \cite{OpenPose}.
 \\
   \newline
-  \indent DeepPose: SOTA pose estimation method that uses DNNs to classify human body joints through the usage of cascading DNN regressors that produce high precision pose estimates [4]. \\
+  \indent DeepPose: SOTA pose estimation method that uses DNNs to classify human body joints through the usage of cascading DNN regressors that produce high precision pose estimates \cite{DeepPos}. \\
   \newline
-  \indent AlphaPose: Multi-person SOTA realtime pose estimation system that outperforms OpenPose in AP score and has a high mAP score [9]. \\
+  \indent AlphaPose: Multi-person SOTA realtime pose estimation system that outperforms OpenPose in AP score and has a high mAP score \cite{Alpha}. \\
   \newline
-  \indent DeepCut: Proposes an approach to solving issues in both pose estimation and detection by using a partitioning and labeling formulation of a set of CNN part detectors [11].
+  \indent DeepCut: Proposes an approach to solving issues in both pose estimation and detection by using a partitioning and labeling formulation of a set of CNN part detectors \cite{DeepCut}.
 \end{quotation}
@@
 recognition equipment, which tends to be expensive and not applicable to how a 
-real game is played, it was decided to use posture recognition via video instead.
+real game is played, it was decided to use posture recognition via video instead \cite{Basketball}.
 In order to improve the athlete's training effect, a gesture recognition method 
@@
 methods, and with the method of feature selection, accurate classification and recognition
-of basketball shooting gestures can be made. This paper is similar to our project because 
+of basketball shooting gestures can be made \cite{Basketball}. This paper is similar to our project because 
 it attempts to take and encode data about motion of a player through pose estimation to 
@@
 Our project will hope to capture and detect objects in high frame-rate video, with minimal computational overhead so that we are able to best assess the keypoints/human joints of our basketball shooters.
-In recent years, object detection algorithms have evolved greatly and most SOTA models today utilize deep learning to provide more robust results [13].
+In recent years, object detection algorithms have evolved greatly and most SOTA models today utilize deep learning to provide more robust results \cite{Viso}.
 There are many pre-existing SOTA object detection methods that have been utilized in the context of pose estimation methods and regression issues, and the following works are examples of some of them.
@@
 \begin{quotation}
-  YOLO: Single stage object detection algorithm that frames detection as a regression problem to spatially seperated bounding boxes and associated class probabilities [3].\\
+  YOLO: Single stage object detection algorithm that frames detection as a regression problem to spatially seperated bounding boxes and associated class probabilities \cite{YOLO}.\\
   \newline
-  \indent Mask R-CNN: Two-stage object detection algorithm that detects objects in an image while creating high-quality segmentation masks for each instance [14].\\
+  \indent Mask R-CNN: Two-stage object detection algorithm that detects objects in an image while creating high-quality segmentation masks for each instance \cite{PatternRec}.\\
   \newline
-  \indent Feature Pyramid Networks: Two-stage object detection algorithm that uses the multi-scale, pyramidial hierarchy of deep convolutional networks to create feature pyramids [15]. \\
+  \indent Feature Pyramid Networks: Two-stage object detection algorithm that uses the multi-scale, pyramidial hierarchy of deep convolutional networks to create feature pyramids \cite{FeaturePyr}. \\
 \end{quotation}
@@
 As far as pose estimation goes, it seems that a bottom up approach to pose estimation will be the best approach for our use case, as the bottom up approach is the
-current state of the art when it comes to pose estimation and is computationally less expensive [12].
+current state of the art when it comes to pose estimation and is computationally less expensive \cite{Datagen}.
 There are a few state of the art bottom up pose estimation libraries that we could potentially use.
@@
 There are three stages we can define: the loading of the shot, the propulsion of the ball from below the waist
-to eye-level, and the release. At these three different stages, we can define three methods for creating feature vectors.
+to eye-level, and the release \cite{FreeThrow}. At these three different stages, we can define three methods for creating feature vectors.
 

### 2022-11-28 Papers/Report/report.tex
Add final report files and revise introduction. Add abstract and work on related works

--- 2022-11-28 Papers/Proposal/PaperForReview.tex
@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{The Shot Predictor}
+\title{Applying Pose Estimation to Predict the Outcome of Basketball Shots}
 
@@
 %%%%%%%%% ABSTRACT
+\begin{abstract}
+  In this report, we present an end-to-end pipeline that includes a pose estimator as well as 
+  a classification model that can effectively predict the outcome of a free throw. Our training data was
+  self-generated by recording hundreds of clips of our test subject shooting free throws of various forms
+  and recording the outcome. We explore different ways to generate feature vectors for inputs to our model as 
+  well as multiple classification models to produce the best performing pipeline.
+\end{abstract}
 
 %%%%%%%%% BODY TEXT
-\section{Problem Description}
+\section{Introduction}
 \label{sec:intro}
@@
 The second reason is the variability of the average shot.
-It can be argued that no two shots are identitical, when taking into account the speed of the shot
-and different shooting forms. This will require us to develop a method of capturing all the motions of a shot in a way that is invariant to the shot's speed and overall form.
-
+It can be argued that no two shots will ever be identical due to the imperfect nature of humans.
+Therefore, it is necessary for our feature representation of a shot to be invariant towards miniscule changes
+in shot form and focus more on fundamental differences.
 %-------------------------------------------------------------------------
@@
 \end{quotation}
+
+Pose estimation attempts to detect the location of 17 keypoints on a human body, as seen in \ref{fig:pose}. These keypoints include key joints such as
+the knee, elbow, shoulder, and wrist, which can be vital in determining the form of a free throw.
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.25\textwidth]{imgs/openpose.png}
+  \caption{Pose estimation keypoints}
+  \label{fig:pose}
+\end{figure}
 %
@@
 
-Collecting and analyzing basketball player's posture data is important and 
-highly sought after in the scientific basketball community in order to help
-coaches improve their training plan, and help players maximize their training 
-outputs. As it stands, the current technology faces some combination of 
-high inefficiency or high error rates. Rather than using wearable, inertial sensor
-recognition equipment, which tends to be expensive and not applicable to how a 
-real game is played, it was decided to use posture recognition via video instead \cite{Basketball}.
-In order to improve the athlete's training effect, a gesture recognition method 
-based on feature extraction and machine learning was implemented in order to 
-acquire the upper limb and lower limb features needed to classify a posture.  
-The action posture data of players was collected through image feature extraction
-methods, and with the method of feature selection, accurate classification and recognition
-of basketball shooting gestures can be made \cite{Basketball}. This paper is similar to our project because 
-it attempts to take and encode data about motion of a player through pose estimation to 
-make predictions, but our project solely focuses on the motion of a shot, and predicting 
-the outcome of the shot.
+The application of pose estimation in basketball is not a new concept. Collecting and analyzing basketball player's
+posture data is an important facet of the scientific basketball community in order to help maximize training outputs.
+For example, pose estimation was used in combination with classification models to predict the action a player is performing
+in a video \cite{Basketball}. This is fairly similar to our project because it attempts to create feature vectors in video frames
+using pose estimation to encode data about the motion of a player and use these features to make a prediction. However, our project
+solely focuses on the motion of a player's shooting form and predicting the outcome of the shot.
 

### 2022-11-28 Papers/Report/report.tex
Add general overview as well as data collection section

@@
 
-Pose estimation attempts to detect the location of 17 keypoints on a human body, as seen in \ref{fig:pose}. These keypoints include key joints such as
+Pose estimation attempts to detect the location of 17 keypoints on a human body, as seen in Figure \ref{fig:pose}. These keypoints include key joints such as
 the knee, elbow, shoulder, and wrist, which can be vital in determining the form of a free throw.
@@
 \subsection{General Overview}
-We will have a camera taking in video input of a player shooting the basketball, potentially from two different angles.
-One angle would be a side view of the shooter that can capture the relative positions of the shooter and the hoop, and the other
-would be a head-on view of the of the shooter to capture the full pose estimation of the shooter.
+% We will have a camera taking in video input of a player shooting the basketball, potentially from two different angles.
+% One angle would be a side view of the shooter that can capture the relative positions of the shooter and the hoop, and the other
+% would be a head-on view of the of the shooter to capture the full pose estimation of the shooter.
 
-In the background, we will have our pose estimation algorithm running to capture the pose estimation of the shooter which will be used
-to make our predictions. Additionally, we will potentially be retrieving other data to create our feature vector, including the angle relationship
-between the shooter and the hoop, and the speed of the shot. We will be attempting to capture the pose estimation at multiple stages of the
-shot, as each stage can have a significant impact on the outcome of the shot. We will then take this feature vector and put it through a classification model.
-We will perform binary classification and predict whether a shot will go in or not.
+% In the background, we will have our pose estimation algorithm running to capture the pose estimation of the shooter which will be used
+% to make our predictions. Additionally, we will potentially be retrieving other data to create our feature vector, including the angle relationship
+% between the shooter and the hoop, and the speed of the shot. We will be attempting to capture the pose estimation at multiple stages of the
+% shot, as each stage can have a significant impact on the outcome of the shot. We will then take this feature vector and put it through a classification model.
+% We will perform binary classification and predict whether a shot will go in or not.
+The high-level overview of our end-to-end pipeline is shown in Figure \ref{fig:flowchart}. We start off by capturing clips of a test subject shooting a free throw. This will be our 
+original data. We first want to downsample the video as we assume that many of the frames will be redundant and take up unnecessary computation time. After this, we perform pose estimation
+on all the frames of each video to get the keypoints of our test subject for each video clip. Using the pose estimation data, we perform
+feature extraction to generate feature vectors for each video clip according to some convention. This will be elaborated on in a later section.
+
+These feature vectors will be the training and testing data that we use for our classification model. We will want to split this data into training
+and testing sets. We will train our classification model on the training set and generate predictions using our testing set.
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.45\textwidth]{imgs/cv_pipeline_real.png}
+  \caption{Overview of Pipeline}
+  \label{fig:flowchart}
+\end{figure}
+
+\subsection{Data Collection}
+To fit the scope of our project, we wanted the shot data be as controlled as possible to prevent unwanted variations
+in our data. To do this, we collected our own data, where we had our test subject always shoot from the free throw line
+and had a camera in a fixed position in front of the test subject to capture their form. The set up can be seen in Figure \ref{fig:ft_data}.
+We genereated approxiamately 300 clips of our test subject shooting free throws. Additionally, for this project, we wanted to detect major changes
+in shooting forms that could affect the outcome of a shot. Therefore, our test subject shot some of their shots as he normally would, with the intent
+of making it, and some of their shots with purposefully bad form, with the intent of missing. We had a relatively even split of these two types of shots.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{imgs/data_collection.png}
+  \caption{Free Throw}
+  \label{fig:ft_data}
+\end{figure}
 

### 2022-11-30 Papers/Report/report.tex
Add most of methodology, add a few papers to the citations, and retrieve up to date scores on the linear classifiers on all the data

@@
 \subsection{Pose Estimation}
-As far as pose estimation goes, it seems that a bottom up approach to pose estimation will be the best approach for our use case, as the bottom up approach is the
-current state of the art when it comes to pose estimation and is computationally less expensive \cite{Datagen}.
-There are a few state of the art bottom up pose estimation libraries that we could potentially use.
-These
-libraries include OpenPose, AlphaPose, DeepCut, and MoveNet. We will test these libraries on their latency and accuracy. With a basketball shot, we want minimum latency
-as well as an ability to run at a high frames per second (FPS) quantity. We will use these metrics as well as an accuracy score on a validation set to determine which pose
-estimation library to use. Once the library is decided, we will include this library into our pipeline to create features from our input video.
+For our pose estimation, we decided between using OpenPose and MoveNet pose estimators.
+These are both bottom up approaches to pose estimation.
+We decided on using bottom up pose estimators as this is the
+current state of the art, and it is computationally less expensive \cite{Datagen}.
+Our first choice was OpenPose, which is considered the SOTA pose estimator.
+However, we found that OpenPose had some issues
+with our data.
+We found that having the basketball greatly hindered the performance of OpenPose detecting our test subject, as seen in Figure \ref{fig:openpose}.
+Additionally, we found OpenPose to be relatively slow
+on the edge compared to MoveNet.
+In contrast, MoveNet was not hindered as much by the basketball and was much faster on the edge.
+Therefore, we decided to move forward with MoveNet as our pose estimator.
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.40\textwidth]{imgs/openpose_bad.png}
+  \caption{OpenPose Pose Detection}
+  \label{fig:openpose}
+\end{figure}
 
-\subsection{Feature Extraction and Classification}
-Before we get into creating features, we need to define how we want to create features using continuous video.
-There are three stages we can define: the loading of the shot, the propulsion of the ball from below the waist
-to eye-level, and the release \cite{FreeThrow}. At these three different stages, we can define three methods for creating feature vectors.
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.40\textwidth]{imgs/movenet_good.png}
+  \caption{MoveNet Pose Detection}
+  \label{fig:movenet}
+\end{figure}
 
-When the shooter loads the ball, the general pose/angle between specific key points is all that matters. However, this stage can take different amounts of time. To combat this,
-we can take the average of each desired angle for the whole time the shooter is at this stage.
+\subsection{Feature Vector Generation}
+Before we can train a classification model to predict the outcome of a shot in a video clip, we need to define how
+we are going to generate the feature vectors for each video clip.
 
-When the shooter is bringing the ball from the loading point to the release point, the movement is more important than key points.
-For example, the movement should not be too fast, and it should generally be straight up.
-Therefore, it would be optimal for us to generate a movement vector for each key point we care about, and also encode the speed component to vectorize this motion.
+As stated previously, we first want to downsample the video to reduce the number
+of frames we are processing, as many of the frames will be redundant. Our initial approach was to
+downsample the video by taking every nth frame, where n is a hyperparameter. However, we soon realized
+that our clips were not all the same length, which would mean we would receive an inconsistent number of
+frames per clip, which could potentially lead to dimensionality issues when we created our feature vectors, depending on our approach.
+To solve this, we decided to take an absolute number of frames per clip, which we decided to be 60.
 
-When the ball is released, the general pose is again more important.
-Additionally, we would like to encode information about the angles between the hoop and the shooter's release point.
-So, for this case, we
-will again use angles of specific key points that we care about in our feature vector as well as information about the relation between the hoop and the shooter.
+After downsampling, we perform pose estimation on each frame of the video clip. Using the pose estimation data, we defined two possible apporaches
+to feature generation:
+\begin{enumerate}
+  \item Concatenate the pose estimation data from each frame of the clip into a single feature vector.
+  \item Use the pose estimation data from each frame of the clip to generate a feature vector for each frame, and perform majority voting the feature vectors to generate the final prediction.
+\end{enumerate}
 
-To perform binary classification, there are two methods we can use.
-We could either concatenate all of these feature vectors and input it into one big classification model that will perform the prediction.
-Alternatively,
-we could put each feature vector through its own classification model and perform some form of weighted majority voting to make our prediction. Both will be tested to determine which method to use.
+Our pose estimator generates a set of 17 two dimensional coordinates, $S=\{(x_1, y_1), (x_2, y_2), \dots, (x_{17}, y_{17})\}$, where each coordinate $(x_i, y_i)$ is the
+position on the image of keypoint $i$. For both approaches on each frame $i$, we concatenate all the coordinates to create a feature vector $v_{ij} \in \mathbb{R}^{34}$, where $v_{ij}$ is
+a feature vector for frame $j$ of clip $i$. For our first approach, we take all the feature vectors for a single clip and concatenate them together, as seen in Figure \ref{fig:feature_vector}.
+This takes 60 feature vectors of 34 dimensions and creates a feature vector $v_i \in \mathbb{R}^{2040}$, where $v_i$ is the feature vector for clip $i$. In contrast, for our second approach, we treat
+each feature vector as a separate data point, and we perform a form of majority voting at the classification stage to generate our final prediction.
+Both of these approaches were tested, and performance
+scores were generated.
 
-We can also test various techniques of classification to see which performs the best.
-We can test between Logistic Regression, Support Vector Machine, Random Forest, and an MLP model.
-We can use cross validation to determine which
-of these model types will be optimal for us.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth, height=0.27\textwidth]{imgs/concat_vectors.png}
+  \caption{First Approach to Feature Vector Generation}
+  \label{fig:feature_vector}
+\end{figure}
 
-\subsection{Training Procedures}
-In order to train our model(s), we will create our own training data by having a subject shoot free throws numerous times, capturing the feature vectors and labelling the data as makes or misses.
+\subsection{Classification Model}
+After we have generated our feature vectors, we used these vectors to train a classification model. We tested various classifiction models such as
+Gradient Boosted Trees (Catboost), Support Vector Machines, Multi-Layer Perceptrons, and K Nearest Neighbors \cite{catboost}\cite{inproceedings}\cite{MURTAGH1991183}. We
+did preliminary testing on the classification models by measuring the performance of each model on our first feature vector approach as a means of 
+choosing the best model for us to do a deeper dive on. To measure the performance of each model, we used accuracy, as generating the AUC score was not 
+feasible for some of the models. Table \ref{tab:table1} shows us the results of each model we tested:
+\begin{table}[h]
+  \begin{center}
+    \caption{Accuracy Scores for Classification Models}
+    \label{tab:table1}
+    \begin{tabular}{l | r}
+      \textbf{Model} & \textbf{Accuracy} \\
+      \hline
+      Catboost Gradient Boosting Tree & 0.636 \\
+      Support Vector Machine & 0.580 \\
+      Multi-Layer Perceptron & 0.556 \\
+      K Nearest Neighbors & 0.602 \\
+    \end{tabular}
+  \end{center}
+\end{table}
 
-\section{Timeline}
-We propose the following timeline, where week 1 represents the week of October 17th:
-\begin{itemize}
-  \item Week 1: \begin{itemize}
-    \item Familiarize ourselves with pose estimation libraries and how to use them.
-    \item Perform tests on each pose estimation library to determin which library to use
-  \end{itemize}
-  \item Week 2: \begin{itemize}
-    \item Collect training data of free throws
-    \item Test our pose estimation library on training data and see the data that we can obtain.
-  \end{itemize}
-  \item Week 3, 4, and 5: \begin{itemize}
-    \item Develop algorithm for feature extraction from shot motion
-    \item Test different types of classification on the data and determine which model to use
-  \end{itemize}
-  \item Week 6: \begin{itemize}
-    \item Evaluate/test final model
-    \item Write final report
-  \end{itemize}
-\end{itemize}
+From the results, we see that the Catboost model got the highest accuracy score. As a result, we chose this model to perform the rest of our experiments on.
 

### 2022-11-30 Papers/Report/report.tex
Start results section

@@
 
+\section{Results}
+In this section, we present and discuss in detail the results of our experiments. In all of these experiments, we used MoveNet as our pose estimator and Catboost
+Gradient Boosting Tree as our classification model, as explained in the previous section.
+\subsection{First Approach to Feature Vector Generation}
+In our first experiment, did a more extensive test on our first approach to feature vector generation. In our preliminary test,
+we did not use our full set of data, as we generated more data after this preliminary experiment. Additionally, we would like to evaluate
+the model on ROC-AUC score. Lastly, as we repeatedly retrained and reevaluated the model, we were getting performance scores that varied 
+to some extent. Because of this, we decided to create a sample distribution of ROC-AUC scores we achieved for each iteration of our model. To do this,
+we ran our model 100 times, each with a randomized train-test split. We then recorded each ROC-AUC score and plotted the histogram of the scores.
 %%%%%%%%% REFERENCES

### 2022-12-01 Papers/Report/report.tex
Add results and analysis of results section

@@
 \usepackage{booktabs}
+\usepackage{adjustbox}
 
@@
 \subsection{First Approach to Feature Vector Generation}
-In our first experiment, did a more extensive test on our first approach to feature vector generation. In our preliminary test,
+In our first experiment, we did a more extensive test on our first approach to feature vector generation. In our preliminary test,
 we did not use our full set of data, as we generated more data after this preliminary experiment. Additionally, we would like to evaluate
@@
 we ran our model 100 times, each with a randomized train-test split. We then recorded each ROC-AUC score and plotted the histogram of the scores.
+Figure \ref{fig:rocauc1} shows the distribution of our ROC-AUC scores for our first approach to feature generation.
+
+% insert figure here
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.45\textwidth]{imgs/approach1_rocauc.png}
+  \caption{Distribution of ROC-AUC Scores for First Approach to Feature Vector Generation}
+  \label{fig:rocauc1}
+\end{figure}
+We produced a mean ROC-AUC score of 0.638, with a standard deviation of 0.043. We also produced a histogram distribution of our accuracy scores, and
+this distribution can be seen in Figure \ref{fig:accuracy1}.
+% insert figure here
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.45\textwidth]{imgs/approach1_acc.png}
+  \caption{Distribution of Accuracy Scores for First Approach to Feature Vector Generation}
+  \label{fig:accuracy1}
+\end{figure}
+We produced a mean accuracy score of 0.570, with a standard deviation of 0.044.
+
+From these results, we see a performance that is better than random guessing, but not by much. Additionally, there is some 
+nontrivial amount of deviation in the performance.
+
+\subsection{Second Approach to Feature Vector Generation}
+In our second experiment, we performed extensive performance tests on our second approach to feature generation. Firstly, we wanted
+to see how effective our classification model would be classifying each frame of every video clip independently as a make or miss.
+This meant we had to label each feature vector for each frame as a make or miss, depending on what the outcome of the clip it originated from.
+We then trained our classification model on this data and evaluated its performance. Like we did before, we ran our model 100 times, each with a randomized train-test split
+and generated a distribution of accuracy scores. We can see the results in Figure \ref{fig:frame_class_results}. From this distribution, we can see that our classification model
+does fairly well in classifying each frame as part of a make clip or a miss clip.
+
+With this in mind, we decided that we could improve performance of predicting the outcome of each clip
+by training the model on singular frames and producing our final prediction by performing some form of a majority vote on each frame for a given clip. This means, to predict the outcome of
+a certain clip, we would input the 60 associated feature vectors into the model foe each frame. We predict the outcome for each of these frames, and if at least half of the frames
+predict a make, our final output will be a make. If at least half of the frames predict a miss, our final output will be a miss.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{imgs/frame_class_results.png}
+  \caption{Distribution of Accuracy Scores for Frame Classification}
+  \label{fig:frame_class_results}
+\end{figure}
+
+We ran this pipeline 100 times to generate a distribution of ROC-AUC scores and accuracy scores. These can be seen in Figure \ref{fig:rocauc2} and Figure \ref{fig:accuracy2} respectively.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.45\textwidth]{imgs/equal_bias_roc.png}
+  \caption{Distribution of ROC-AUC Scores for Equal Weighted Majority Voting}
+  \label{fig:rocauc2}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.45\textwidth]{imgs/equal_bias_acc.png}
+  \caption{Distribution of Accuracy Scores for Equal Weighted Majority Voting}
+  \label{fig:accuracy2}
+\end{figure}
+
+We achieved a mean ROC-AUC score of 0.794 with a standard deviation of 0.063 and a mean accuracy score of 0.726
+with a standard deviation of 0.068. Though the standard deviation is slightly higher, the overall performance of this approach seems
+to be much better than our first approach, with both ROC-AUC and accuracy scores increasing significantly.
+
+\subsection{Tuning the Majority Voting Threshold}
+After evaluating majority voting with equal weights, we wanted to see if we could improve the performance of this by tuning the threshold of our majority vote.
+We tried three different thresholds: 0.25, 0.5, and 0.75.
+For
+each threshold we, again, ran 100 iterations and generated a distribution of ROC-AUC scores and accuracy scores.
+The statistics of the distributions for each of the thresholds can be seen in Table \ref{tab:table2} and Table \ref{tab:table3}.
+
+\begin{table}
+  \begin{center}
+    \begin{adjustbox}{width=0.47\textwidth}
+    \begin{tabular}{|c|c|c|}
+      \textbf{Threshold} & \textbf{Mean of ROC-AUC} & \textbf{Standard Deviation of ROC-AUC} \\
+      \hline 
+      0.25 & 0.795 & 0.067  \\
+      0.50 & 0.794 & 0.063  \\
+      0.75 & 0.793 & 0.058  \\
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Statistics of ROC-AUC Majority Voting Threshold Experiments}
+    \label{tab:table2}
+  \end{center}
+\end{table}
+\begin{table}
+  \begin{center}
+    \begin{adjustbox}{width=0.47\textwidth}
+    \begin{tabular}{|c|c|c|}
+      \textbf{Threshold} & \textbf{Mean of Accuracy} & \textbf{Standard Deviation of Accuracy} \\
+      \hline 
+      0.25 & 0.679 & 0.072  \\
+      0.50 & 0.726 & 0.068  \\
+      0.75 & 0.688 & 0.062  \\
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Statistics of Accuracy Majority Voting Threshold Experiments}
+    \label{tab:table3}
+  \end{center}
+\end{table}
+
+We see that the mean ROC-AUC score is highest for a threshold of 0.25, but only by a very small margin. In general, the ROC-AUC scores are quite similar, but it is clear
+that when measuring performance by accuracy, the threshold of 0.5 tends to perform the best. The combination of the ROC-AUC scores and accuracy scores lead us to believe that
+the threshold of 0.5 is the best choice.
+
+\subsection{Modifying Majority Voting Criteria}
+Our final experiment was to see if we could improve performance of the majority voting by using the median of the soft probability scores instead of the mean. This was done in
+an attempt to reduce the effect of outliers on the vote. Again, we ran this 100 times and generated a performance score distribution. We attempted to use three different thresholding
+values for this as well. The statistics of the ROC-AUC scores and accuracy scores
+
+\begin{table}[h]
+  \begin{center}
+    \begin{adjustbox}{width=0.47\textwidth}
+    \begin{tabular}{|c|c|c|}
+      \textbf{Threshold} & \textbf{Mean of ROC-AUC} & \textbf{Standard Deviation of ROC-AUC} \\
+      \hline 
+      0.25 & 0.783 & 0.057  \\
+      0.50 & 0.798 & 0.053  \\
+      0.75 & 0.793 & 0.059  \\
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Statistics of ROC-AUC Median Voting Threshold Experiments}
+    \label{tab:table4}
+  \end{center}
+\end{table}
+\begin{table}[h]
+  \begin{center}
+    \begin{adjustbox}{width=0.47\textwidth}
+    \begin{tabular}{|c|c|c|}
+      \textbf{Threshold} & \textbf{Mean of Accuracy} & \textbf{Standard Deviation of Accuracy} \\
+      \hline 
+      0.25 & 0.688 & 0.057  \\
+      0.50 & 0.733 & 0.054  \\
+      0.75 & 0.663 & 0.078  \\
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Statistics of Accuracy Median Voting Threshold Experiments}
+    \label{tab:table5}
+  \end{center}
+\end{table}
+
+From this, we see that a threshold value of 0.5 for the median voting performs marginally better, but not significantly
+enough to make a real difference.
+
+\section{Analysis}
+From our experiments we concluded that our second approach to feature generation and classification was
+far more successful than our first approach. We believe that the main issue with our first approach was
+insufficient data. We were only able to generate about 300 total clips, which meant we had about 210
+feature vectors to train on and 90 to test on. This simply was not enough data to train a robust classifier.
+
+When we trained the model on all the frames, we had a much larger dataset to train on, as each clip would give us 60
+feature vectors. This gives the model more of a chance to learn patterns in the data to make its predictions.
+
+A deeper dive into our second approach to feature vector generation shows us that a threshold of 0.50 for the majority vote
+performs the best, and a median vote goes not significantly change the performance.
+
+\section{Conclusion}
+
 %%%%%%%%% REFERENCES

### 2022-12-01 Papers/Report/report.tex
Finish first draft of paper

@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{Applying Pose Estimation to Predict the Outcome of Basketball Shots}
+\title{Applying Pose Estimation to Predict the Outcome of A Free Throw}
 
@@
 
+\subsection{Other Explorations}
+After achieving these results, we explored other methods that have historically been useful in improving the performance of
+classification models. Principal Component Analysis (PCA) was the first method we explored to attempt to find the most significant
+features of our features. However, when we performed the PCA transform, we greatly hindered the performance of our model to about the
+performance of random guessing.
+
+Additionally, we attempted stacking models together to improve our performance. We stacked many different classification models together
+and attempted to use the majority voting method to improve the performance. However, this also hindered the performance of our model.
+
 \section{Analysis}
+\subsection{Performance Analysis}
 From our experiments we concluded that our second approach to feature generation and classification was
@@
 
-\section{Conclusion}
+\subsection{Pitfalls and Issues}
+Although we were able to achieve adequate performance metrics with our approach, there are still some issues that
+our current method cannot overcome.
+
+\subsubsection{Invariance to Camera Position}
+
+One of the main issues with our current approach is that our feature vector generation highly sensitive to the position of our camera. For our data collection,
+we held the camera in a fixed position to record our test subject shooting free throws, and our feature vectors used the absolute coordinates of each of the 17 key points
+to create our feature vector for a frame. This means that if we were to move the camera, or even if the person were to move, the feature vectors would be completely different, 
+even if the shooting form is the same.
+
+In order to fix this issue, we could use relative coordinates, fixing one of the key points as the origin, and calculating the relative coordinates of the other 16 key points.
+This would allow our feature representation to be more invariant to the position of the camera or the test subject. Additionally, we could use a feature representation that took into
+account the angles between the key points because the angles of joints are very important in determining the form of a shot. Using the angles would also make the feature representation
+not depend on the absolute position.
+
+\subsubsection{Loss of Temporal Information}
+
+In our current representation, we are performing a majority vote on all the frames of a clip, but when we do this, we lose all temporal information and the sequential nature of the shot.
+This means, theoretically, we could shuffle the frames of the clip, or even reverse the video, and the model will still predict the same.
+
+In order to capture the sequential
+nature of the shooting form, it would have been beter to potentially use a recurrent neural network to capture the temporal information.
+
+\section{Conclusion and Future Works}
+In this paper, we attempted to leverage pose estimation to help predict the outcome of a free throw. This involved collecting data
+of a test subject shooting free throws, and using the pose estimation to generate feature vectors, and training a 
+classification model to predict the outcome of a shot.
+
+Through this process, we learned a great deal about how pose estimation works and the methodology behind generating feature vectors from data as well as
+the nuances of training classification models.
+
+Future works for this project would be to imrpove the robustness of our feature vector generation and capturing the temporal information, as explained 
+in the previous section. Additionally, we could explore extending this project to work at different locations on the court and for different people shooting.
+Lastly, we could explore the possibility of performing the prediction in real time, so that the results can be produced live instead of from a video recording.
 
